RDF Constraints Classification Ensuring \\ High Quality of Metadata and Data

### 2015-04-18 paper/paper7/paper7.tex
introduction

% Todos
\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}
\newcommand{\er}[1]{\todo[size=\small, color=red!40]{\textbf{Erman:} #1}}
\newcommand{\an}[1]{\todo[size=\small, color=blue!40]{\textbf{Andy:} #1}}

@@

\section{Motivation}
\label{motivation}

The data most often used in research within the SBE community is \emph{person-level data}, i.e. data collected about individuals, businesses, and households in form of responses to studies or taken from administrative registers
(such as hospital records, registers of births and deaths). 
The range of person-level data covers many different domains and is very broad - 
including census, education, and health data as well as all types of business, social, and labor force surveys.  
Increasingly, this type of research data is
held within data archives or data libraries after it has been collected, so that it may be
reused by future researchers. 
In performing their research, the detailed person-level
data is aggregated into less confidential multi-dimensional tables which answer particular research questions.
Portals harvest metadata (as well as publicly available data) from multiple data providers in form of RDF.
To ensure high quality, the metadata must satisfy certain criteria - specified in terms of RDF constraints.  
After validating the metadata according to these constraints, portals offer added values to their customers, e.g. by searching over and comparing metadata of multiple providers.

@@

%\section{Running Example}
%\label{running-example}
\section{Vocabularies to Represent Metadata and Data in RDF}
\label{rdf-representation}

\textcolor{red}{figure / metadata: person-level, aggregated, thesauri, catalogs, statistical classifications / data: rectangular data}

@@

\tb{aut SDMX sind year, duration, age, etc. keine Variablen, sondern Dimensionen}

@@

In this section, we describe constraints and constraint types which are important to ensure (meta)data  quality on different aggregation levels. 
Furthermore, we associate constraints with default severity levels and assign them to validation types.

We recently published a technical report\footnote{\textcolor{red}{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as first appendix of this paper) in which we describe and classify constraints to validate rectangular data and metadata on person-level data sets, aggregated data sets, thesauri, and statistical classifications and therefore apply the proposed classification system \cite{BoschZapilkoWackerowEckert2015}.

@@

\subsection{Content-Driven Constraint Types}
\label{content-driven-validation}

\tb{die einzelnen Paragraphen sollten constraint types clustern entsprechen - Unterkapitel umorganisieren!}

\textcolor{red}{short description}

@@

\section{Conclusion and Future Work}

In this paper, we showed in form of a complete real world running example how to represent metadata on person-level data (\emph{Disco}), metadata on aggregated data (\emph{QB}), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
We explained why RDF validation is important in this context and how metadata on person-level data, aggregated data, thesauri, and statistical classifications as well as data on both aggregation levels is validated against constraints to ensure high (meta)data quality\footnote{The first appendix of this paper describing each constraint in detail is available at: \textcolor{red}{\url{http://arxiv.org/abs/XXXXX}} \cite{BoschZapilkoWackerowEckert2015}} (\textbf{contribution 2}, section \ref{rdf-validation}). 
We distinguish two validation types:
(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of data models (section \ref{content-driven-validation}).
(2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges (section \ref{technology-driven-validation}).
We determined the default \emph{severity level} for each constraint to indicate how serious the violation of the constraint is
and propose an extensible metric to measure the continuum of severity levels.

>>>>

% Todos
\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\ke}[1]{\todo[size=\small, color=red!40]{\textbf{Kai:} #1}}
\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}
\newcommand{\er}[1]{\todo[size=\small, color=blue!40]{\textbf{Erman:} #1}}

@@

\section{Motivation}
\label{motivation}
\ke{@KAI: Dieses Kapitel werde ich noch deutlich kürzen!}
The data most often used in research within the SBE community is \emph{person-level data}, i.e. data collected about individuals, businesses, and households in form of responses to studies or taken from administrative registers
(such as hospital records, registers of births and deaths). 
The range of person-level data covers many different domains and is very broad - 
including census, education, and health data as well as all types of business, social, and labor force surveys.  
Increasingly, this type of research data is
held within data archives or data libraries after it has been collected, so that it may be
reused by future researchers. 
In performing their research, the detailed person-level
data is aggregated into less confidential multi-dimensional tables which answer particular research questions.
Portals harvest metadata (as well as publicly available data) from multiple data providers in form of RDF.
To ensure high quality, the metadata must satisfy certain criteria - specified in terms of RDF constraints.  
After validating the metadata according to these constraints, portals offer added values to their customers, e.g. by searching over and comparing metadata of multiple providers.

@@

%\section{Running Example}
%\label{running-example}
\section{Vocabularies to Represent Metadata and Data in RDF}
\label{rdf-representation}
\ke{@KAI: Dieses Kapitel werde ich noch deutlich kürzen!}
\tb{figure / metadata: person-level, aggregated, thesauri, catalogs, statistical classifications / data: rectangular data}

@@

\tb{laut SDMX sind year, duration, age, etc. keine Variablen, sondern Dimensionen}

@@

We recently published a technical report\footnote{\textcolor{red}{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as first appendix of this paper) in which we describe and classify constraints to validate rectangular data and metadata on person-level data sets, aggregated data sets, thesauri, and statistical classifications and therefore apply the proposed classification system \cite{BoschZapilkoWackerowEckert2015}.
In this section, we describe constraint types and constraints which are important to ensure (meta)data  quality on different aggregation levels. 
Furthermore, we associate constraints with default severity levels and assign them to validation types.

@@

\subsection{Content-Driven Constraint Types}
\label{content-driven-validation}
\ke{@KAI: Dieses Kapitel werde ich noch umorganisieren! Die einzelnen Paragraphen sollten zusammengehörigen Clustern von constraint types entsprechen!}

\tb{short description}

@@

\section{Conclusion and Future Work}
\ke{@KAI: Dieses Kapitel muss ich noch an die Änderungen im Paper anpassen!}
In this paper, we showed in form of a complete real world running example how to represent metadata on person-level data (\emph{Disco}), metadata on aggregated data (\emph{QB}), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
We explained why RDF validation is important in this context and how metadata on person-level data, aggregated data, thesauri, and statistical classifications as well as data on both aggregation levels is validated against constraints to ensure high (meta)data quality\footnote{The first appendix of this paper describing each constraint in detail is available at: \textcolor{red}{\url{http://arxiv.org/abs/XXXXX}} \cite{BoschZapilkoWackerowEckert2015}} (\textbf{contribution 2}, section \ref{rdf-validation}). 
We distinguish two validation types:
(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of data models (section \ref{content-driven-validation}).
(2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges (section \ref{technology-driven-validation}).
We determined the default \emph{severity level} for each constraint to indicate how serious the violation of the constraint is
and propose an extensible metric to measure the continuum of severity levels.
